Automated Verification and Synthesis of Cyber-Physical Systems: Advances and Challenges

### 2018-03-25 paper.tex
IET CPSTA

{\textbf{(RP6)} State-of-the-art synthesis approaches for embedded (control) systems typically disregard the platform in which the embedded system software operates and restrict themselves to generate code that do not take into account FWL effects. The synthesized system, however, must include the physical plant to avoid serious system's malfunctioning (or even a catastrophe), due to the embedded (control) software, {\it e.g.}, the Mars Polar Lander did not account for leg compressions prior to landing~\cite{Jackson16}. Research in this direction has made some progress to design, implement, and evaluate an automated approach for generating correct-by-construction digital controllers that is based on state-of-the-art inductive synthesis techniques~\cite{Abate17,abatecav2017}. Nonetheless, there is still little evidence whether that approach can scale for larger systems modeled by other types of representation ({\it e.g.}, Multiple-Input Multiple-Output). In addition to that, another research direction for synthesizers is to generate code for UAV trajectory and mission planning by taking into account system's dynamics and nonholonomic constraints~\cite{Araujo16}. As a consequence, verifiers and synthesizers need to handle a wide range of functions, including non-linear and non-convex optimization problems based on both fixed- and floating-point arithmetic.

@@

As already mentioned in section \ref{sec:model}, problems that are not directly related to code correctness may be tackled with formal methods, as long as they are conveniently modeled. Ara\'ujo {\it et al.} \cite{Araujo16} employed SMT for handling non-convex optimization problems, with the goal of ensuring optimal solutions. Indeed, it is possible to recursively re-constrains a model checking procedure, by using the current counterexample as a seed for the next run, until a global minimum is achieved. Nonetheless, elapsed execution times are still a bottleneck for some applications, such as changes in UAV trajectories, but that can be improved, through the use of simplification techniques and problem constraints.

In the same fashion, other problems may benefit from the recursive-refinement approach provided by SMT-based verification schemes. For instance, de Jesus {\it et. al} \cite{antennasbrt} developed a simplified methodology for antenna alignment that makes use of many modules already available in satellite TV receivers, along with a suitable structure for performing position correction. In summary, a reference signal is evaluated, until an (approximately) error-free reception is acquired, which can be measured through a simple transport stream (TS) error-indication interface and further refined with other parameters, such as carrier-to-noise ratio and signal level. This way, by using an SMT-based verification method, one may map the TS error indication and other performance figures as properties and then recursively perform realignment procedures, until a counterexample is not output. It is worth noticing that associated timing requirements are more relaxed than what was mentioned in the work developed by Ara\'ujo {\it et al.}~\cite{Araujo16}, which can be seen as an advantage for such an implementation.

>>>>

{\textbf{(RP6)} State-of-the-art synthesis approaches for embedded (control) systems typically disregard the platform in which the embedded system software operates and restrict themselves to generate code that do not take into account FWL effects. The synthesized system, however, must include the physical plant to avoid serious system's malfunctioning (or even a catastrophe), due to the embedded (control) software, {\it e.g.}, the Mars Polar Lander did not account for leg compressions prior to landing~\cite{Jackson16}. Research in this direction has made some progress to design, implement, and evaluate an automated approach for generating correct-by-construction digital controllers that is based on state-of-the-art inductive synthesis techniques~\cite{Abate17,abatecav2017}. Nonetheless, there is still little evidence whether that approach can scale for larger systems modeled by other types of representation ({\it e.g.}, Multiple-Input Multiple-Output). In addition to that, another research direction for synthesizers is to generate code for UAV trajectory and mission planning by taking into account system's dynamics and nonholonomic constraints~\cite{ARAUJO2017}. As a consequence, verifiers and synthesizers need to handle a wide range of functions, including non-linear and non-convex optimization problems based on both fixed- and floating-point arithmetic.

@@

As already mentioned in section \ref{sec:model}, problems that are not directly related to code correctness may be tackled with formal methods, as long as they are conveniently modeled. Ara\'ujo {\it et al.} \cite{ARAUJO2017} employed SMT for handling non-convex optimization problems, with the goal of ensuring optimal solutions. Indeed, it is possible to recursively re-constrains a model checking procedure, by using the current counterexample as a seed for the next run, until a global minimum is achieved. Nonetheless, elapsed execution times are still a bottleneck for some applications, such as changes in UAV trajectories, but that can be improved, through the use of simplification techniques and problem constraints.

In the same fashion, other problems may benefit from the recursive-refinement approach provided by SMT-based verification schemes. For instance, de Jesus {\it et. al} \cite{antennasbrt} developed a simplified methodology for antenna alignment that makes use of many modules already available in satellite TV receivers, along with a suitable structure for performing position correction. In summary, a reference signal is evaluated, until an (approximately) error-free reception is acquired, which can be measured through a simple transport stream (TS) error-indication interface and further refined with other parameters, such as carrier-to-noise ratio and signal level. This way, by using an SMT-based verification method, one may map the TS error indication and other performance figures as properties and then recursively perform realignment procedures, until a counterexample is not output. It is worth noticing that associated timing requirements are more relaxed than what was mentioned in the work developed by Ara\'ujo {\it et al.}~\cite{ARAUJO2017}, which can be seen as an advantage for such an implementation.
